Deep Learning Models For Identifying Crop and Field Attributes from Near Surface Cameras

### 2021-12-15 manuscript/main.tex
add figure 1 annotations

\begin{figure}[H]
    \includegraphics[width=14.5cm]{fig1_example_images.jpg}
    \caption{Example images from the PhenoCam network used in this study. The images are from the cameras arsope3ltar on Sep. 17, 2018 (A), cafcookwestltar01 on Aug. 15, 2017 (B), kelloggcorn on Nov. 27, 2018 (C), arsltarmdcr on Aug. 28, 2017 (D), mandanh5 on June 27, 2017 (E),  arsgacp1 on Aug. 25, 2016 (F), NEON.D06.KONA.DP1.00033 on Dec. 24, 2017 (G), hawbeckereddy on Nov. 26, 2015 (H), and bouldinalfalfa on Oct. 22, 2019 (I).
}
    \label{fig1}
\end{figure}

>>>>

\begin{figure}[H]
    \includegraphics[width=14.5cm]{fig1_example_images.jpg}
    \caption{Example images from the PhenoCam network used in this study. The image sources and annotations are as follows: (A) is from arsope3ltar on Sep. 17, 2018 with soybeans in the growth stage, (B) is from cafcookwestltar01 on Aug. 15, 2017 with wheat which is fully senesced, (C) is kelloggcorn on Nov. 27, 2018 and is blurry for all categories, (D) is arsltarmdcr on Aug. 28, 2017 with corn in the flowers stage, (E) is from mandanh5 on June 27, 2017 and has corn in the growth stage with a dominant cover of residue, (F) is from arsgacp1 on Aug. 25, 2016 with dominant cover of plant residue and no crop present, (G) is from NEON.D06.KONA.DP1.00033 on Dec. 24, 2017 with dominant cover of snow and no crop present, (H) is from hawbeckereddy on Nov. 26, 2015 with an unknown crop type in the growth state, and (I) is from bouldinalfalfa on Oct. 22, 2019 with a dominant cover of residue and no crop present. Images A, B, D, and H all have vegetation as the dominant cover class.
}
    \label{fig1}
\end{figure}
